% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Varoun. P}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{https://github.com/varoun}
 \moveleft.5\hoffset\centerline{varoun@varoun.com}
 \moveleft.5\hoffset\centerline{+919980499930}

 
\begin{resume} 
 

\section{Experience}
 {\bf Tech Yahoo,} Yahoo! Bangalore \hfill Feb 2006 - Dec 2009
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Service Engineering Lead for various Yahoo! properties including
   MyBlogLog. Responsibilities included capacity planning, setting up 
   automated deployment, setting up monitoring, providing oncall production
   support, and working with developers to ensure that system
   architecture met production engineering \\ standards.
 \item Unix System Admin for very large installations of FreeBSD and RHEL.
   Responsibilities included user management, bringing new hosts online, 
   troubleshooting performance problems, setting up and administering the 
   Yahoo! authoritative and recursive name servers, administering dns 
   zone files, administering edge \\ services and geographical load balancing
   amongst others.
 \item Incident Manager and Tier2 engineer at the Yahoo! Network Operations 
   Center / Operations Center. Responsibilities included taking full ownership
   of production outages, coordinating the efforts of the different teams 
   involved in the resolution  process and communicating the current status 
   to senior management and \\ partners.
   
 \end{itemize}

 
 
{\bf Associate Engineer,} TATA Consultancy Services, Madras. \hfill June 2005 - Jan 2006
 \begin{itemize} \itemsep -2pt %reduce space between items
 \item Consultant engineer for Motorola. Worked on SCM, automated build and 
   deployment systems.
 \item Setup technical controls to ensure SOx compliance. 

 \end{itemize}

{\bf Sr. Tech Executive,} Software Technology Group, Madras. \hfill Dec 2003 - May 2005
 \begin{itemize} \itemsep -2pt
 \item Handled Red Hat's RHCE training program at STG. STG received the Red Hat
   award for maximum enrollments during this time.
 \item Consulted with clients on migrating from proprietary application stacks
   to LAMP. Handled migrations from MS Exchange to open solutions running on 
   Linux / FreeBSD.
   
 \end{itemize}

{\bf Unix System Admin Intern,} DynaSource, Madras. \hfill June 2003 - Nov 2003
 \begin{itemize} \itemsep -2pt
 \item Responsible for setup, routine administration and troubleshooting 
   of LAMP \\ application, email and DNS infrastructure.
   
 \end{itemize}

\section{Technical Expertise} 
 \begin{itemize} \itemsep -2pt
 \item Unix system administration with specific focus on Linux and FreeBSD.
 \item Setup, administration and tuning of http (Apache), email (Postfix, Cyrus imapd)
   DNS (BIND) and Database (MySQL, PostgreSQL, SQLite) servers.
 \item Engineering internet scale, distributed, and fault tolerant systems 
   using a combination of geographical load balancing (Akamai), hardware load 
   balancers, edge services/caches (Yahoo! Traffic Server) and database replication 
   amongst others.
 \item Setup and administration of SNMP and Nagios for infrastructure monitoring.
 \item Automating routine administration tasks.
 \item Programming in Common Lisp, Scheme, and Bourne shell.
 \item Programming RESTful webservices - both clients and servers.
   
 \end{itemize}

\section{Education} 
Bachelor of Engineering, Instrumentation and Control Systems.\\
University of Madras, 2003.


\end{resume} 
\end{document} 
